Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-08 acl.2016/acl2016.tex
acl paper

\subsection{Core Affinity}

The phrase-based decoding algorithm requires fast access to memory in order to 
Core affinity enables the binding of specific threads to specific CPU cores.

>>>>

\subsection{Scalability}

\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{scalability.png}} 
\end{tabular}
\caption{Decoding speed}
\label{fig:speed}
\end{figure}

Figure~\ref{fig:speed} shows decoding speed against the number of threads, measured in words translated per second. Speed increases linearly with 2 threads as each thread is run on separate physical processors. The translation rate only decrease slightly with every additional threads until 16 threads are used which produces a 12.5 times faster than single-threaded decoding. The need to share resources such as CPU cache and internal bus bandwidth is probably responsible for the non-linear increase in speed.

Since the test server only has 16 real cores, additional threads must be run on the same physical cores as existing threads. This further constrains the resources that each thread has, therefore we see a markedly lower speed increase with each additional thread once there are more than 16 concurrent threads.

Overall though, the scalability is remarkably good, the decoder is able to make full use of all real and virtual cores. When all cores are saturated, the decoder is 16 times faster than single-threaded decoding, on this 16 real core server.

This contrast with Moses which scales to approximately 16 threads but then actually become slower if more are used, Figure~\ref{fig:moses-speed}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-scalability.png}} 
\end{tabular}
\caption{Moses decoding speed}
\label{fig:moses-speed}
\end{figure}
